---
title: "Sound and Synthesis"
output: 
  revealjs::revealjs_presentation:
    theme: black
    transition: slide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Welcome

## What we think of when we talk about synthesizers {data-background="Yamaha_DX7_Table_4.JPG"}

## What is sound?

## {data-background="Spherical_pressure_waves.gif"}

## Sine wave

```{r}
library(ggplot2)
x <- seq(0,50,.1)
d = data.frame(x=x,y=sin(x))
ggplot(data = d) + geom_line(mapping = aes(x = x, y = y)) + xlab("time") + ylab("amplitude") + theme(axis.ticks = element_blank(), axis.text = element_blank())
```

## Another sine wave

```{r}
library(ggplot2)
x <- seq(0,50,.1)
d = data.frame(x=x,y=-sin(x))
ggplot(data = d) + geom_line(mapping = aes(x = x, y = y)) + xlab("time") + ylab("amplitude") + theme(axis.ticks = element_blank(), axis.text = element_blank())
```

## More waves {data-background="Waveforms.svg"}

## {data-background="ADSR_parameter.svg"}

## "patch"

**a.** _trans_. To connect by a temporary electrical, radio, or telephone connection; (also) to represent or simulate by means of temporary connections; usu. with _in_, _into_, _through_; _spec_.  _(a)_ to connect (a telephone call, or the person making it) to a telephone circuit;  _(b)_ to set the controls of (a synthesizer) so as to produce a particular sound; to produce (a sound) by this means. **to patch out:** to disconnect from a circuit by diverting current through a temporary connection.

[1923   _Bell Syst. Techn. Jrnl._ **2** 123   In open-wire installations it has been the practice to equip each line circuit..with a full complement of jacks suited to provide the maximum degree of flexibility in ‘patching’.] 